The ChEMBL database as Linked Open Data

### 2013-03-26 article.tex
add comma to split sentence up
grammar fix

Some information in the databases has not yet been annotated using standard ontologies. 
For example, the activity types in ChEMBL, such as ``IC50'', ``EC50'', and ``Potency'', are not exposed in the RDF dataset,
meaning that it is not yet possible to reason or group over similar activity types.
When the activity types are exposed queries could be constructed based on the knowledge 
that the IC$_{50}$ and K$_i$ end points are closely related. Similarly, measurement units are currently provided as
string literals, making it difficult to compare concentrations when some are given in nM and others in mM.
In the future it may also be possible, relying on some assumptions, to crossmatch activities
expressed in $\mu$g/ml with query concentrations in nM. These additional semantics are necessary 
to translate raw experimental data into semantically useful, machine-readable information.

@@

Finally, the ChEMBL team (JO, AG, MD) plans to be a primary source of a RDF version of ChEMBL, while others continue
exposing ChEMBL as RDF too (EW, PA). Various version may arise, exposing the data in different ontologies,
supporting current community needs, however, convergence is expected after a period of experimenting with ontologies that
may not prove to be practically useful. The availability of Open Source scripts ensures that the community can contribute to the
process of choosing a practically useful set of ontological terms.

>>>>

Some information in the databases has not yet been annotated using standard ontologies. 
For example, the activity types in ChEMBL, such as ``IC50'', ``EC50'', and ``Potency'', are not exposed in the RDF dataset,
meaning that it is not yet possible to reason or group over similar activity types.
When the activity types are exposed, queries could be constructed based on the knowledge 
that the IC$_{50}$ and K$_i$ end points are closely related. Similarly, measurement units are currently provided as
string literals, making it difficult to compare concentrations when some are given in nM and others in mM.
In the future it may also be possible, relying on some assumptions, to crossmatch activities
expressed in $\mu$g/ml with query concentrations in nM. These additional semantics are necessary 
to translate raw experimental data into semantically useful, machine-readable information.

@@

Finally, the ChEMBL team (JO, AG, MD) plans to be a primary source of a RDF version of ChEMBL, while others continue
exposing ChEMBL as RDF too (EW, PA). In the future various versions may arise, exposing the data in different ontologies,
supporting current community needs, however, convergence is expected after a period of experimenting with ontologies that
may not prove to be practically useful. The availability of Open Source scripts ensures that the community can contribute to the
process of choosing a practically useful set of ontological terms.
